A game-theory modeling approach to utility and strength of interactions dynamics in biomedical research social networks

### 2016-11-07 manuscript_3.tex
reviewed from the beginning thru Methodology
Mostly corrected verb tenses and removed lots of chaff.

What would happen if researchers in a community were given the same amount of
resources and then set free to interact among each other? How would these
resources be distributed in the population after many interactions? The final
result may be determined by the researchers'social and political power, an by
her or his prestige. Nevertheless, all these attributes depend, to a 
certain degree, on the research collaboration social network in which scientists
are embedded. Here we develop a model based on the Prisoner's Dilemma
implemented on a collaboration network. With this model we explore the
distribution of resources and the dynamics of the strengthening or weakening of collaboration
connections among partners, as scientists cooperate or
defect in order to gain access to others resources. The network is based on data
about projects that were awarded with a grant. In this sense, we assume that
resources are funds, equipment and time. Fitness, as we define it here
represents how much access does a researcher has over the resources of its collegues.  
We tested our simulation on the real biomedical research network and compared
the results with an Erd\"{o}s-Reny\'i, a Watts-Strogatz small-world
and Barab\'asi-Albert topologies. Different topologies display different fitness
and connections strength distributions. Moreover, the distribution of fitness
and connections strength in the researchers network is similar to that of Barab\'asi-Albert 
and Watts-Strogatz topologies, respectively. We believe that fitness
distribution in the researchers network suggests that there are socio-cultural
mechanisms governing the network that produces asymmetric distribution to
resources. Nevertheless, the high distribution of strong connections might reflect some sort of
subordination among researchers by which they are morally obliged to cooperate
by the same socio-cultural mechanisms. The range around the threshold that
regulates the decision to cooperate or defect according to the agent's
historical balance between utility and strength of collaborative relationships and carring
capacity of the system is small, suggesting that there is a region in which a
phase transition takes place from a population of cooperators to a population of
defectors. Simulations like this may help to develop science policies to promote
fair distribution of resources.

@@

Collaboration has become a corner stone in biomedical research today.
In contrast to physics which has a long history and experience in collaborative
projects, biology has only recently become an evermore collaborative
discipline\cite{Vermeulen2013}. Biology has an interesting record in such
matters because scientific collaboration means something different to
different branches of biology: molecular biology has traditionally been a
research activity of small laboratories\cite{KnorrCetina1999,Strasser2006},
whereas in natural history there has been data and samples exchange since the
$XVII^{th}$ century\cite{Muller2012,Strasser2012}.\\

Despite the differences in culture and practices, the Human Genome
Project made collaboration a central feature of biology. Nowadays it
is widely acknowledged that collaboration takes many forms, from
biological samples and biobanking to international groups in charge of
helping the bio-research communities to harmonize and share their
data. Collaboration in science may take many forms, nevertheless, sharing
resources such as equipment, funds, and time are critical; also, building
trust among scientists is fundamental. What is more important, resources are
mobilized in order to create strategic alliances.\\

The analysis of cooperation in scientific research has been the subject of a
number of studies
\cite{Vermeulen2013,Newman2001,Newman2004,Elango2012,HernandezLemus2013,Strasser2006,Strasser2012}. This
is not surprising since cooperation and competition are quite important in
today's academic success. How do collaboration happens within a competitive
academic environment and what kind of payoff is present in these settings were
questions considered recently by Wardil and Hauert \cite{Wardil2015} in the
context of cooperation in multi-authored publications. Also, the role of game
theory over complex scientific information and collaboration networks has
attracted attention, mainly focusing on how long-term strategies may shape
different scenarios for Nash equilibria \cite{hanauske2012}. Prisoner's Dilemma
has been used in the study of impact factor and collaboration
\cite{Hara_etal_2002,Lieberman_etal_2005}. \\

In spite of all these research efforts, cooperation in the context of scientific
collaboration is still loosely defined and the long time dynamics of academic
cooperation (and its consequences) are yet to be fully elucidated. Furthermore,
to our current knowledge, we are not aware of the use of game theory and
the complex network analysis for understanding how the topology of scientific collaboration networks
affects access to resources among individuals present in the network \footnote{For
  an account of scientific collaboration and definitions, please refer to
  \cite{Sonnenwald2007}.}. In this context our work aims to contribute to
further our current understanding on the matte, specially when agents have to
maximize their acces to resources while they need to take care of their collaboration links.\\

@@

 {\color{red}In this article we explore the network effect on the distribution
   of players having access to certain amount of resources from other players in the
   network and the distribution of the strength of connections among
   them. Particularly, we implemented two games played simultaneously: 
   one for maximazing individual utility based on the iterated Prisoner's
   dilemma; the other, a coordination game for maximazing the connection strength between
   players. We are interested in how they affect each other in 
   the context of a network of scientific collaboration under the idea that while
   researchers are interested in maximazing their utilities, they also know that
   it is important to invest in building collaborative relationships. These two
   behaviors are explored in a biomedical research community of M\'exico.}\\

{\color{red}In the context of our paper, utility represents
  the preference for having access to the resources of others. Maximazing
  utility means that the player is increasing its access to the resources of
  other players.  Utility function is the sum of the payoffs of playing
  with its neighbors. The opossing force is in the other game. The game for
  maximazing the strength of the connection among players. In this case
  coordinating is the best strategy as it pays the most when
  coordinating regardeless they both cooperate or defect, this is because when
  both cooperate the interaction gets a positive payoff, when both defect, the
  interaction doesn't get affected; but if they anti-coordinate, then the
  interaction looses. Finally, cooperation is a central feature in science
  doing. For our biomedical network, cooperation can be metaphorically thought
  as sharing resources such as time, students, equipment, even money. Defection
  to a cooperator may also have some examples, such as ghost authorship or
  prestige authorship, or even a part of a working strategy in which a some
  members of a team do the work at certain moment, and then the other part of
  the team will do its part in some other moment in the future --some sort of
  reciprocity. }\\

The manuscript is structured in five sections. The following describes
\textit{FOSISS}, the main program for grants destined for biomedical applied
research in M\'exico. This description is important because that is the source
of our database for creating the researchers collaboration network. Next we
describe our model, and then, in the following section we introduce the
different network topologies on which we explored the model. In the fourth
section we present  our results and discuss them briefly. In the fifth section
we draw some final remarks and conclusions.

@@

CONACyT (National Council of Science and Technology) is the Mexican government
entity in charge of promoting the development of science and 
technology. It is also in charge of creating the country's scientific
policies.  Among CONACyT's functions are to develop science and technology
policies according to national needs and demands, to advise the different
instances of government on scientific and technological topics, to promote the
creation of research networks among the scientific community, to grant
scholarships for masters and doctoral studies, and to manage different trusts 
intended to fund individuals and groups for scientific and
technological research.\\

In the year 2002 CONACyT, along with other government agencies and
entities, created sectoral funds which are trusts for scientific and
technological research.The objective of such funds is to cover and equally
promote the research capacities of different areas such as energy, agriculture,
or technological innovation by means of the generation of human resources
and helping research groups to consolidate. It is expected that the
knowledge generated under the sponsorship of these funds
will be the product of applied research that attends national public
needs, and promotes economic growth.\\

\emph{FOSISS} or Sectoral Fund for Health and Social Security Research
(\emph{Fondo Sectorial en Investigaci\'on en Salud y Seguridad Social}) is among
such funds. FOSISS is constituted by CONACyT, SSA, IMSS and ISSSTE,\footnote{SSA
  is the acronym for Secretariat of Health \emph{Secretar\'ia de Salud}; IMSS is
  the acronym for Social Security Mexican Institute (\emph{Instituto Mexicano
    del Seguro Social}); ISSSTE stands for Institute for Social Security and
  Services for State Workers (\emph{Instituto de Seguridad y Servicios Sociales
    de los Trabajadores del Estado})} being all of them the major public health
providers and research institutions in the country. Every year CONACyT opens a
call for funds limited to a set of health research areas previously defined by a
group of experts. Such areas range from public health issues to chronic and
degenerative diseases.\\

Eligibility is open to the public and private health research sectors,
nevertheless, most applicants are public universities and research
institutions. Up to the year of 2013, there were 91 institutions funded that
comprised 4988 researchers.\\

From these data some important considerations should be made clear. The
population represented in the data include principal investigators (PIs),
associate researchers, postdoctoral associates, under and postgraduate
students. Unfortunately, this information is not specified in the
database. Still, this is something we acknowledge and it's important because
researchers in our network are under different circumstances and we know
that this diversity has a real impact on the structure and eventually on the
dynamics of the network, as well as on the results of our model.\\

Our database includes different information about the projects. It includes the
name of the project, the year it was approved for funding, and the research area
to which it was assigned. It also specifies the names of PIs or the person who
was responsible of a project, the names of those who have been collaborators,
some PIs have also been collaborators of a different project. The institutional
affiliation of all participants can be found too. This is important because
knowing the affiliation of the researcher we also know the principal institution
behind every project.\\

Though, cleaning and analysis work of the database is still ongoing, some
relevant facts about the biomedical research can be said. Over the period of 12
years, 32 general research areas have been defined, the three most funded
research areas are \emph{chronic and degenerative diseases}, \emph{malignant
  neoplasms}, and \emph{infectious and parasitic diseases}. The least funded
area is \emph{Ethics and medicine}. But the areas with more researchers is
\emph{malignant neoplasms}. Other areas of relevance for M\'exico are
\emph{diseases related to poverty} and \emph{Health and vulnerable groups}. \\

From the institutions that have participated in a protocol funded by FOSISS,
less than one fifth has been responsible for a project and more than 95\% of
them are Mexican, public institutions. There is also an important presence of
foreign institutions as collaborators, most of them from the United States,
though institutions from the UK, France, Spain, Netherlands, Colombia and Cuba
are also in the database.\\

Besides the characteristics of the population there are some other boundary
conditions that play an important role on the network topology and dynamics,
that motivated the development of our model. Biomedical research in M\'exico
constitutes a vibrant community and collaboration is part of everyday
work. Nevertheless, M\'exico does not have public biobanks for research purposes
(which are specially relevant for research in genomics, for example), there is
no regulation on the access to biological samples such as tissue, cells, DNA,
RNA, etc.\footnote{Regulation exists regarding researcher-subject relations
  based on legal and ethical grounds. Also, all projects need to be approved by
  the Ethics Committee and IRB.} Something similar happens with data. There have
been some attempts to create open data repositories for biomedical research, but
they have not been established yet. Regulation on these subjects is still
missing. Finally, technology (e.g., PCR, sequencing and expression profiling
technology) is in the domain of the institutions with the highest research
profiles and sometimes PIs see technology as a personal good.\\

From our brief ethnographic work to date, we have been able to see that
biological samples, data and technology can become instruments for negotiating
collaboration. For example, among people involved in research projects, there
are researchers that do not have direct access to samples, simply because their
institution does not offer clinical services. Many of them are non medical
doctors but chemists, biologists, physicists, and mathematicians. There is
another group of researchers that are placed on hospitals who are able to do
research and have access to biological samples from their own patients. It seems
that this group is the most privileged one, and the least pressured to establish
collaboration at whatever cost. Finally, there is one more group formed by those
who work as clinicians at small hospitals with no research infrastructure
whatsoever. This group may have an interest in research and the way for them to
become part of a project and be listed as authors in scientific papers is by
giving researchers who do not have access to biological samples access to
patients.\\

Due to these differences in the access to resources, researchers in
general are compelled to build strategic alliances through which samples, data,
technology and authorship, among others, become part of a constant flow through
the network. Social and political capital, as well as concentrations of
resources become fundamental tools for establishing fruitful collaborations.

@@

Our model is based on the iterated version of the Prisoner's Dilemma (PD) and a
coordination game instantiated on
networks. Implementing games on networks is not new and it's an active area of
research aimed to understand the evolution of cooperation in networks populated
by selfish agents \cite{Szabo2007,Nowak1992,Nowak2006,Santos2005,Santos2006}. In many network models
on which some of game theory games are simulated, agents' decision to cooperate
or defect depend on a specific strategy, such as the well known
\textit{tit-for-tat} \cite{Axelrod2006,Nowak2011}. In some other cases, agents
can modify the weight of the interactions with their neighbors
\cite{Santos2006}. From a different perspective others have explored the effect
of different topologies on the emergence of cooperation
\cite{Santos2005,Hauert2004}. {\color{red}In our case, agents' decision to cooperate or
defect is an outcome that depends on the agent's balance between
utilities and the current strength of its collaboration relationships. Such
balance reflects the overall success or failure of its strategies}. We
study the behavior of the system under different topologies, including a
real-world network.\\

@@

{\color{red} It should be noticed that the same actions or behaviors work for
  both $u$ and $w$. There are two reasons for this decision in the design of the
model. The most general one is that we believe that in the real world,
actions such as cooperating and defecting affect the strength of the connection
among people. The second one is that we think that selfishly maximizing resources and
strenghting relationships as \emph{opposing forces} acting on the same set of
behaviors. The actions of an agent imply a trade-off in which defecting may
increase its utility at the expense of its collaborative relationships. If
collaborators have nurished their relationship, it might be strong enough to
endure occasional defection. Cooperating may build up relationships but it can be
expensive for the player.}

>>>>

  What would happen if researchers in a community were given the same
  amount of resources and then set free to interact among each other?
  How would these resources be distributed in the population after
  many interactions? The final result may be determined by the
  researchers' social and political power, an by their
  prestige. Nevertheless, all these attributes depend, to a certain
  degree, on the research collaboration social network in which
  scientists are embedded. Here we develop a model based on the
  Prisoner's Dilemma implemented on a collaboration network. With this
  model we explore the distribution of resources and the dynamics of
  the strengthening or weakening of collaboration connections among
  partners, as scientists cooperate or defect in order to gain access
  to others' resources. The network is based on data about projects
  that were awarded with a grant. In this sense, we assume that
  resources are funds, equipment and time. We define Fitness as how
  much access a researcher has to the resources of his collegues.  We
  tested our simulation on the real biomedical research network and
  compared the results with an Erd\"{o}s-Reny\'i, a Watts-Strogatz
  small-world and Barab\'asi-Albert topologies. Different topologies
  display different fitness and connections strength
  distributions. Moreover, the distribution of fitness and connections
  strength in the researchers network is similar to that of
  Barab\'asi-Albert and Watts-Strogatz topologies, respectively. We
  believe that fitness distribution in the researchers network
  suggests that there are socio-cultural mechanisms governing the
  network that produce an asymmetric distribution of resources. The
  high distribution of strong connections might reflect some sort of
  subordination among researchers by which they are morally obliged to
  cooperate by the same socio-cultural mechanisms. The range around
  the threshold that regulates the decision to cooperate or defect
  according to the agent's historical balance between utility and
  strength of collaborative relationships and carrying capacity of the
  system is small, suggesting that there is a region in which a phase
  transition takes place from a population of cooperators to a
  population of defectors. Simulations like this may help to develop
  science policies to promote fair distribution of resources.

@@

Collaboration has become a cornerstone in biomedical research today.
In contrast to physics which has a long history and experience in
collaborative projects, biology is only recently becoming an evermore
collaborative discipline\cite{Vermeulen2013}. Biology has an
interesting record in such matters because scientific collaboration
means something different to different branches of biology: molecular
biology has traditionally been a research activity of small
laboratories\cite{KnorrCetina1999,Strasser2006}, whereas in natural
history there has been data and samples exchange since the $XVII^{th}$
century\cite{Muller2012,Strasser2012}. Despite the differences in
culture and practices, the Human Genome Project made collaboration a
central feature of biology.\\

Nowadays it is widely acknowledged that collaboration takes many
forms, from sharing of biological samples and biobanking to
international groups in charge of helping research communities to
harmonize and share their data. Sharing resources such as equipment,
funds, and time is critical; building trust among scientists is
fundamental. Also, resources are mobilized in order to create strategic alliances.\\

The analysis of cooperation in scientific research has been the subject of a
number of studies
\cite{Vermeulen2013,Newman2001,Newman2004,Elango2012,HernandezLemus2013,Strasser2006,Strasser2012}. This
is not surprising since cooperation and competition are quite important in
today's academic success. How does collaboration happen within a competitive
academic environment and what kind of payoff is present in these settings were
questions considered recently by Wardil and Hauert \cite{Wardil2015} in the
context of cooperation in multi-authored publications. Also, the role of game
theory over complex scientific information and collaboration networks has
attracted attention, mainly focusing on how long-term strategies may shape
different scenarios for Nash equilibria \cite{hanauske2012}. Prisoner's Dilemma
has been used in the study of impact factor and collaboration
\cite{Hara_etal_2002,Lieberman_etal_2005}. \\

Even with all these research efforts, cooperation in the context of
scientific collaboration is still loosely defined and the long term
dynamics of academic cooperation (and its consequences) are yet to be
fully elucidated. Furthermore, to our current knowledge, there has
been no use of game theory and complex network analysis for
understanding how the topology of scientific collaboration networks
affects access to resources among individuals present in the network
\footnote{For an account of scientific collaboration and definitions,
  please refer to \cite{Sonnenwald2007}.}. Our work aims to contribute
to our current understanding on the matter, specially when agents have
to maximize their access to resources while taking care of their collaboration links.\\

@@

 {\color{red}In this article we explore the network effect on the distribution
   of players having access to certain amount of resources from other players in the
   network and the distribution of the strength of connections among
   them. Particularly, we implemented two games played simultaneously: 
   one for maximazing individual utility based on the iterated Prisoner's
   Dilemma; the other, a coordination game for maximazing the connection strength between
   players. We are interested in how they affect each other in 
   the context of a network of scientific collaboration under the idea that while
   researchers are interested in maximazing their utilities, they also know that
   it is important to invest in building collaborative relationships. These two
   behaviors are explored in a biomedical research community of M\'exico.}\\

{\color{red}In the context of our paper, utility represents
  the preference for having access to the resources of others. Maximazing
  utility means that the player is increasing its access to the resources of
  other players. The value of the Utility function for a player is the sum of the payoffs of playing
  with his neighbors. The opossing force comes from the other concurrent game: players
  trying to maximize the strength of their connections to other players. In the coordinating game
  the best strategy is to adopt the same strategy as the other player, as it pays the most
  regardless of cooperation or defection in the utility game. When
  both cooperate the interaction gets a positive payoff, when both defect, the
  interaction doesn't get affected; but if they anti-coordinate, then the
  interaction looses. Finally, cooperation is a central feature of scientific work.
  For our biomedical network, cooperation can be thought of
  as sharing resources such as time, students, equipment, even money. Examples of defection
  to a cooperator are ghost authorship or
  prestige authorship.

  % este ejemplo de defection no es nada claro:
  %
  % Another example may be a working strategy in which some
  % members of a team do the work at certain moment, and then another part 
  % does its part in some other moment in the future --some sort of
  % reciprocity.

}\\

The manuscript is structured in five sections. First we describe
\textit{FOSISS}, the main program for grants destined to biomedical applied
research in M\'exico. This is the source of the
database from which we created the researchers collaboration network. Next we
describe our model
and the different network topologies on which we explored it.
We then present our results and discuss them briefly. In the last section
we draw some final remarks and conclusions.

@@

CONACyT (National Council of Science and Technology) is the Mexican government
entity in charge of promoting the development of science and 
technology.
Among CONACyT's functions are to develop science and technology
policies according to national needs and demands, to advise the different
instances of government on scientific and technological topics, to promote the
creation of research networks among the scientific community, to grant
scholarships for masters and doctoral studies, and to manage different trusts 
intended to fund individuals and groups for scientific and
technological research.\\

In the year 2002 CONACyT, along with other government agencies and
entities, created sectoral funds
to cover and equally
promote research capacities of different areas such as energy, agriculture
and health. Technological innovation is fostered by the generation of human resources
and by helping research groups to consolidate. It is expected that the
knowledge generated under the sponsorship of these funds
will be the product of applied research that attends national public
needs, and promotes economic growth.\\

\emph{FOSISS} or Sectoral Fund for Health and Social Security Research
(\emph{Fondo Sectorial en Investigaci\'on en Salud y Seguridad Social}) is one of
such funds. FOSISS is constituted by CONACyT, SSA, IMSS and ISSSTE,\footnote{SSA
  is the acronym for Secretariat of Health \emph{Secretar\'ia de Salud}; IMSS is
  the acronym for Social Security Mexican Institute (\emph{Instituto Mexicano
    del Seguro Social}); ISSSTE stands for Institute for Social Security and
  Services for State Workers (\emph{Instituto de Seguridad y Servicios Sociales
    de los Trabajadores del Estado})} being all of them the major public health
providers and research institutions in the country. Every year CONACyT opens a
call for funds limited to a set of health research areas previously defined by a
group of experts. Such areas range from public health issues to chronic and
degenerative diseases.\\

Eligibility is open to public and private health research sectors,
however most applicants are public universities and research
institutions. From 2002 through 2013, there were 91 institutions funded that
comprised 4988 researchers.\\

From these data some important considerations should be made clear. The
population represented in the data include principal investigators (PIs),
associate researchers, postdoctoral associates, postgraduate and undergraduate
students.
% wut? which information is not specified? which is pi and which is undergrad is not specified?
Unfortunately, this information is not specified in the
database. Still, this is something we acknowledge and it's important because
researchers in our network are under different circumstances and we know
that this diversity has a real impact on the structure and eventually on the
dynamics of the network, as well as on the results of our model.\\

Our database includes the
name of the project, the year it was approved for funding and the research area
to which it was assigned. It specifies the names of PIs or the people 
responsible for the project and the names of collaborators.
Researchers can be PIs in one project and collaborators on a different project. The institutional
affiliation of all participants is included. Through this affiliation
we know the principal institution
behind every project.\\

Even though curation and analysis work of the database is still ongoing, some
relevant facts about the biomedical research can be said. Over the period of 12
years, 32 general research areas have been defined, the three most funded
research areas are \emph{chronic and degenerative diseases}, \emph{malignant
  neoplasms}, and \emph{infectious and parasitic diseases}. The least funded
area is \emph{Ethics and medicine}. The area with the most researchers is
\emph{malignant neoplasms}. Other areas of relevance for M\'exico are
\emph{diseases related to poverty} and \emph{Health and vulnerable groups}. \\

From the institutions that have participated in a protocol funded by FOSISS,
less than one fifth have been responsible for a project and more than 95\% of
them are Mexican, public institutions. There is also an important presence of
foreign institutions as collaborators, most of them from the United States,
though institutions from the UK, France, Spain, Netherlands, Colombia and Cuba
are also in the database.\\

Besides the characteristics of the population there are some other boundary
conditions that play an important role on the network topology and dynamics,
that motivated the development of our model. Biomedical research in M\'exico
constitutes a vibrant community and collaboration is part of everyday
work. However, M\'exico does not have public biobanks for research purposes
(which are specially relevant for research in genomics, for example), there is
no regulation on the access to biological samples such as tissue, cells, DNA,
RNA, etc.\footnote{Regulation exists regarding researcher-subject relations
  based on legal and ethical grounds. Also, all projects need to be approved by
  the Ethics Committee and IRB.} Something similar happens with data. There have
been some attempts to create open data repositories for biomedical research, but
they have not been established yet. Regulation on these subjects is still
missing. Finally, technology (e.g., PCR, sequencing and expression profiling
technology) is in the domain of the institutions with the highest research
profiles and sometimes PIs see technology as a personal good.\\

From our ethnographic work to date, we have been able to see that
biological samples, data and technology can become instruments for negotiating
collaboration. For example, among people involved in research projects, there
are researchers that do not have direct access to samples, simply because their
institution does not offer clinical services. Many of them are non medical
doctors but chemists, biologists, physicists, and mathematicians. There is
another group of researchers that are placed on hospitals who are able to do
research and have access to biological samples from their own patients. It seems
that this group is the most privileged one, and the least pressured to establish
collaboration at whatever cost. Finally, there is one more group formed by those
who work as clinicians at small hospitals with no research infrastructure
whatsoever. This group may have an interest in research and the way for them to
become part of a project and be listed as authors in scientific papers is by
giving researchers who do not have access to biological samples access to
patients.\\

Due to these differences in the access to resources, researchers in
general are compelled to build strategic alliances through which samples, data,
technology and authorship, among other assets, become part of a constant flow through
the network. Social and political capital, as well as concentrations of
resources become fundamental tools for establishing fruitful collaborations.

@@

Our model is based on the iterated version of the Prisoner's Dilemma (PD) and a
coordination game instantiated on
networks. Implementing games on networks is not new and it's an active area of
research aimed to understand the evolution of cooperation in networks populated
by selfish agents \cite{Szabo2007,Nowak1992,Nowak2006,Santos2005,Santos2006}. In many network models
on which some of game theory games are simulated, agents' decision to cooperate
or defect depend on a specific strategy, such as the well known
\textit{tit-for-tat} \cite{Axelrod2006,Nowak2011}. In some other cases, agents
can modify the weight of the interactions with their neighbors
\cite{Santos2006}. From a different perspective others have explored the effect
of different topologies on the emergence of cooperation
\cite{Santos2005,Hauert2004}. {\color{red}In our case, an agent's decision to cooperate or
defect is an outcome that depends on a balance between
utilities and the current strength of its collaboration relationships. Such
balance reflects the overall success or failure of its strategies}. We
study the behavior of the system under different topologies, including a
real-world network.\\

@@

{\color{red} It should be noted that the same actions or behaviors work for
  both $u$ and $w$. There are two reasons for this decision in the design of the
model. The most general one is that we believe that in the real world,
actions such as cooperating and defecting affect the strength of the connection
among people. The second one is that we think that selfishly maximizing resources and
strenghting relationships are \emph{opposing forces} acting on the same set of
behaviors. The actions of an agent imply a trade-off in which defecting may
increase its utility at the expense of its collaborative relationships. If
collaborators have nourished their relationships, they might be strong enough to
endure occasional defection. Cooperating may build up relationships but it can be
expensive for the player.}
